Estimating Evolutionary Parameters for Protein Low Complexity Regions using an Approximate Bayesian Computation

### 2022-11-28 beap_pres_dec2022/beap_pres_dec.tex
Nov 27 UPDATES PART 2 8:00 pm

% Theme choice: there a number of preset themes to choose from
% Play around with them, Cambridge is nice for first pres
%\usetheme{Szeged}
\usetheme{CambridgeUS} %setting the main theme
%\usecolortheme{beaver} % setting colour theme
\usefonttheme{professionalfonts} %font theme
%\useinnertheme{} %inner theme
%\useoutertheme{} %outer theme

%\setbeamertemplate{footline} %Remove footer line in all slides
\setbeamertemplate{navigation symbols}{} %removes navigation symbols
\setbeamertemplate{footline}[page number] %removes footer line, keeps pg#

%Setting colours for boxes
\setbeamercolor{block title}{bg=darkred, fg=white}
\setbeamercolor{block body}{bg=darkred!10}

%Trying this out for captions
\setbeamertemplate{caption}{%
	\begin{beamercolorbox}[wd=.5\columnwidth, sep=.2ex]{block body}\insertcaption%
	\end{beamercolorbox}%
}

@@

@@

		\begin{center}
			\includegraphics[width=5cm, height=1cm]{poyglut.png}
		\end{center}

@@

		\begin{center}
			\includegraphics[width=5cm, height=1cm]{direpeat.png}
		\end{center}

@@

			\column{0.5\textwidth}
			\centering
			\begin{figure}
				\includegraphics[width=\columnwidth, height=2.5cm]{slippage2.png} \\~\\
				\caption{\centering Polymerase Slips Forward}
			\end{figure}

			\column{0.5\textwidth}
			\centering
			\begin{figure}
				\includegraphics[width=\columnwidth, height=2.5cm]{slippage1.png} \\~\\
				\caption{\centering Polymerase Slips Backwards}
			\end{figure}

@@

@@

	%For my Research questions/Exploration slides, I will talk about things such as
	%SLIDE 9%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Research Questions/Exploration}
	\begin{frame}{What will this Study Explore?}

@@

@@

		\begin{enumerate}
			\item Propose a move from $\theta$ to $\theta'$ according to the normal distribution
			\item Create a random protein sequence and mutate over many generations using $\theta'$ to generate simulated Dataset $D'$
			\item Calculate summary statistics for simulated dataset $D'$ 
			\item If $d(S',S) \le \epsilon$, go to next step, otherwise stay at $\theta$ and return to 1
			\item Accept $\theta'$ with probability ?? Ask Brian ab this again lol
			\item Return to step 1
		\end{enumerate}

>>>>

% Theme choice: there a number of preset themes to choose from
% Play around with them, Cambridge is nice for first pres
%\usetheme{Szeged}
\usetheme{CambridgeUS} %setting the main theme
%\usecolortheme{beaver} % setting colour theme
\usefonttheme{professionalfonts} %font theme
\useinnertheme[shadow=true]{rounded}
%\useoutertheme{} %outer theme

%\setbeamertemplate{footline} %Remove footer line in all slides
\setbeamertemplate{navigation symbols}{} %removes navigation symbols
\setbeamertemplate{footline}[page number] %removes footer line, keeps pg#
\setbeamertemplate{caption}{\insertcaption}

%Setting colours for boxes and captions
\setbeamercolor{block title}{bg=darkred, fg=white}
\setbeamercolor{block body}{bg=darkred!10}

% For the Flowchart
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}
\tikzstyle{startstop} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=red!30]
\tikzstyle{process} = [rectangle, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=orange!30]
\tikzstyle{decision} = [diamond, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=green!30]
\tikzstyle{arrow} = [thick,->,>=stealth]

@@

%For itemize
\setbeamertemplate{itemize item}[triangle]

@@

		\begin{center}
			\includegraphics[width=5cm, height=1cm]{poyglut.png}
		\end{center} \pause

@@

		\begin{center}
			\includegraphics[width=5cm, height=1cm]{direpeat.png}
		\end{center} \pause

@@

			\column{0.5\textwidth}
			\centering
			\begin{figure}
				\includegraphics[width=\columnwidth, height=2.5cm]{slippage2.png} \\~\\
				\caption{\centering \textbf{Polymerase Slips Forward}}
			\end{figure}

			\column{0.5\textwidth}
			\centering
			\begin{figure}
				\includegraphics[width=\columnwidth, height=2.5cm]{slippage1.png} \\~\\
				\caption{\centering \textbf{Polymerase Slips Backwards}}
			\end{figure}

@@

	\begin{center}	
		\begin{tikzpicture}[node distance=2cm]
			\node[startstop] (1) {Disease};
			\node[startstop, right of=1, xshift=2cm] (2) {Biological Processes};
			\node[startstop, right of=2, xshift=2cm] (3) {Presence in Bacteria};
			\node[startstop, above=2, xshift=4cm, yshift=1cm] (4) {LCR's};

			\draw [arrow] (4) -- (1);
			\draw [arrow] (4) -- (2);
			\draw [arrow] (4) -- (3);

		\end{tikzpicture}
	\end{center}

		\begin{columns}

			\column{0.33\textwidth}
			\centering
			\begin{figure}
				\includegraphics[width=\columnwidth, height=2.5cm]{huntington.jpg} \\~\\
				\caption{\centering \textit{Huntington's Disease}}
			\end{figure}

			\column{0.33\textwidth}
			\centering
			\begin{figure}
				\includegraphics[width=2.5cm, height=2.5cm]{chrom.png} \\~\\
				\caption{\centering \textit{Genetic Recombination}}
			\end{figure}

			\column{0.33\textwidth}
			\centering
			\begin{figure}
				\vspace{-0.4cm}
				\includegraphics[width=\columnwidth, height=2.5cm]{menin.jpg} \\~\\
				\caption{\centering \textit{Neisseria meningitidis}}
			\end{figure}

@@

	%For my Research questions/Exploration slides, I will talk about things such as
	%SLIDE 9%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Research Questions/Exploration}

	\begin{frame}{What will this Study Explore?}
		\begin{itemize}
			\item Estimation of evolutionary parameters (mutation rate, indel rates) \newline
			\item Various models of insertions and deletions \newline
			\item Summary statistics which best explain data
		\end{itemize}

@@

		\footnotetext[3]{\tiny\cite{marjoram2003markov}}	
	\end{frame}

@@

		\begin{enumerate}
			\item Propose a move from $\theta$ to $\theta'$ according to the normal distribution \pause
			\item Create a random protein sequence and mutate over many generations using $\theta'$ to generate simulated Dataset $D'$ \pause
			\item Calculate summary statistics for simulated dataset $D'$ \pause
			\item If $d(S',S) \le \epsilon$, go to next step, otherwise stay at $\theta$ and return to 1 \pause
			\item Accept $\theta'$ with probability ?? Ask Brian ab this again lol \pause
			\item Return to step 1
		\end{enumerate}
